Designing an Active Vision Indoor Object Search Guidance System

### 2018-11-05 paper.tex
Fixed some small captions and titles I forgot about

\usepackage{siunitx}
\usepackage{tikz}

\usetikzlibrary{calc,arrows.meta,intersections,backgrounds,shapes.misc}

@@

\title{Designing an Indoor Guidance System for the Visually Impaired}

@@

\keywords{Active vision, vision impaired, Markov decision process, object search}

\abstract{In this work, we propose an active vision system that uses a Markov Decision Process and mobile phone to enable a user to find an object in an unknown environment. This project aims to deliver a workable system to the visually impaired, but a set of experiments were carried out with sighted participants to determine the effectiveness of the system. We found that the system works reasonably well and compares well to similar systems. However, some improvements are required before it is ready for real-world use. }

@@

\noindent We are designing an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or find an object in an unknown and dynamic environment, expanding upon ideas originally proposed in~\cite{bellotto2013} and expanded on in~\cite{lock2017portable}. The proposed system implements ideas from the active vision field and places a human in the control loop. This control loop, pictured in Figure~\ref{fig:control-loop}, comprises of a controller, $K$, that is given a reference signal (the desired objects in this case) that generates a control signal, $u$, which a human, $H$, uses to manipulate a sensor, $P$, to gather more information on the environment and move closer to the target object. %The goal of this system is to automatically make sense of the user's surroundings and determine the optimal route to get to the final destination based on what the user/camera sees, thereby roughly emulating a normally sighted user's navigation strategy in an unknown environment.

In this paper we discuss the first steps we have taken into implementing the control-block, $K$, from Figure~\ref{fig:control-loop}. The goal of this system is to understand the user's surroundings and determine what the next best course of action is to reach the target location, based on what the system is currently seeing and what it has seen in the past. We used a Markov Decision Process (MDP)~\cite{bellman1957markovian} to produce a so-called policy that defines the optimal action, $a$, our agent (the guidance system in this case) takes when it is in some state $s$.

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{figures/control_loop.png}
  \caption{MEME}\label{fig:control-loop}
\end{figure}

@@

Section~\ref{sec:previous-work} discusses other relevant work done in this field, followed by a detailed discussion on the design of the guidance system, human-control module and MDP\@ in Sections~\ref{sec:system-design} and~\ref{sec:controller-design}. Then we discuss the experiment and present its results in Section~\ref{sec:experiments}, after which we conclude the paper and discuss the project's next steps in Section~\ref{sec:conclusion}.

@@

\begin{table}
  \centering
  \caption{MEME}\label{tab:rewards}
  \begin{tabular}{ll}
    \toprule
    $s\in\mathbf{S}$ & -1.0  \\ \midrule
    $s(n >= 9)$ & -10.0 \\ \midrule
    $s(v = 1)$  & -10.0 \\ \midrule
    $s(o = \text{target})$ & 10000 \\ \midrule
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{figure}
  \centering
  \begin{subfigure}
    \centering
    \includegraphics[width=0.4\textwidth]{figures/desk_example.png}
  \end{subfigure}
  \begin{subfigure}
    \centering
    \includegraphics[width=0.4\textwidth]{figures/mug_example.png}
  \end{subfigure}
  \caption{MEME~\cite{openimages}}\label{fig:openimage-example}
\end{figure}

>>>>

\usepackage{siunitx}
%\usepackage{tikz}

%\usetikzlibrary{calc,arrows.meta,intersections,backgrounds,shapes.misc}

@@

\title{Designing an Active Vision Indoor Object Search Guidance System}

@@

\keywords{Active vision, object search, vision impaired, Markov decision process}

\abstract{In this work, we propose an active vision system that uses a Markov Decision Process and mobile phone to enable a user to find an object in an unknown environment. An initial implementation of this system was implemented and tested with a set of experiments were carried out with sighted participants to determine the effectiveness of the system. We found that the system works reasonably well and compares well to similar systems. }

@@

\noindent We are designing an indoor navigation system (ActiVis) targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or find an object in an unknown and dynamic environment, expanding upon ideas originally proposed in~\cite{bellotto2013} and expanded on in~\cite{lock2017portable}. The proposed system implements ideas from the active vision field and places a human in the control loop. This control loop, pictured in Figure~\ref{fig:control-loop}, comprises of a controller, $K$, that is given a reference signal (the desired objects in this case) that generates a control signal, $u$, which a human, $H$, uses to manipulate a sensor, $P$, to gather more information on the environment and move closer to the target object. %The goal of this system is to automatically make sense of the user's surroundings and determine the optimal route to get to the final destination based on what the user/camera sees, thereby roughly emulating a normally sighted user's navigation strategy in an unknown environment.

In this paper we discuss the first steps we have taken into implementing the control-block, $K$, from Figure~\ref{fig:control-loop}. The goal of ActiVis is to understand the user's surroundings and determine what the next best course of action is to reach the target location, based on what the it is currently seeing and what it has seen in the past. We used a Markov Decision Process (MDP)~\cite{bellman1957markovian} to produce a so-called policy that defines the optimal action, $a$, our agent (the guidance system in this case) takes when it is in some state $s$.

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{figures/control_loop.png}
  \caption{The ActVis system layout and control loop. }\label{fig:control-loop}
\end{figure}

@@

Section~\ref{sec:previous-work} discusses other relevant work done in this field, followed by a detailed discussion on the design of the ActiVisguidance  system, human-control module and MDP\@ in Sections~\ref{sec:system-design} and~\ref{sec:controller-design}. Then we discuss the experiment and present its results in Section~\ref{sec:experiments}, after which we conclude the paper and discuss the project's next steps in Section~\ref{sec:conclusion}.

@@

\begin{table}
  \centering
  \caption{A table containing the model rewards for our MDP. }\label{tab:rewards}
  \begin{tabular}{ll}
    \toprule
    $s\in\mathbf{S}$ & -1.0  \\ \midrule
    $s(n >= 9)$ & -10.0 \\ \midrule
    $s(v = 1)$  & -10.0 \\ \midrule
    $s(o = \text{target})$ & 10000 \\ \midrule
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{figure}
  \centering
  \begin{subfigure}
    \centering
    \includegraphics[width=0.4\textwidth]{figures/desk_example.png}
  \end{subfigure}
  \begin{subfigure}
    \centering
    \includegraphics[width=0.4\textwidth]{figures/mug_example.png}
  \end{subfigure}
  \caption{Examples of images from the OpenImage dataset containing objects from $\mathit{O}$~\cite{openimages}}\label{fig:openimage-example}
\end{figure}
